### 2018-01-04 Writing/disparity_review.tex
review up

Similarly, many studies in geometric morphometric are based solely on skull shape using landmark techniques combined with Procrustes sumperimposition \citep[the ``\texttt{geomorph}'' approach;][]{zelditch2012geometric,adams2017geometric}.
However, it has been shown that the whole skeleton displays different integrated modules with different specific evolutionary constraints leading to variable rates and modes of evolution (\citealt{Goswami20130254}; and this even at the cranial level \citealt{goswami2010influence}).
Is skull variation enough for measuring body plans variation through time for example?

@@

\section{Is the current statistical toolkit sufficient for testing disparity hypothesis?}
Are the methods used to test hypothesis in disparity actually testing what we think they’re testing (problem of multidimensional hypothesis)
What does an anova or related variance based test real infirms/confirms regarding the disparity questions?
How do we deal with bootstrapped data and pseudo-replications?
Can we realistically use univariate gaussian models to test hypothesis based on multivariate, probably non-gaussian data? \citep{blomberg2017beyond}

>>>>

Similarly, many studies in geometric morphometric are based solely on skull shape using landmark techniques combined with Procrustes superimposition \citep[the ``\texttt{geomorph}'' approach;][]{zelditch2012geometric,adams2017geometric}.
However, it has been shown that the whole skeleton displays different integrated modules with different specific evolutionary constraints leading to variable rates and modes of evolution (\citealt{Goswami20130254}; and this even at the cranial level \citealt{goswami2010influence}).
Is skull variation enough for measuring body plans variation through time for example?

@@

\section{Is the current statistical toolkit sufficient for testing disparity hypothesis?}
Are the methods used to test hypothesis in disparity actually testing what we think they’re testing (problem of multidimensional hypothesis)
What does an anova or related variance based test real infirm/confirms regarding the disparity questions?
How do we deal with bootstrapped data and pseudo-replications?
Can we realistically use univariate Gaussian models to test hypothesis based on multivariate, probably non-Gaussian data? \citep{blomberg2017beyond}
